Object Categorization based on RGBD data

### 2013-09-28 Disseration/article.tex
a

\section{BoW based image classification}

\subsection{Detection}
\subsection{Description}
\subsection{Vector Quantization}
\subsection{Classification}

>>>>

\section{BoW based classification}

	The Bag of Words intermediate image represenation provides a concise way of summarizing images. It is invariant to affaine transformations, partial occlusion and, in some extent, to changing lighting conditions. What is more, it is easy to implement and computationally efficient. The efficiency can be enhanced even further with gpu based implementations as shown in \cite{van2011empowering}. In order to incorporate BoW into an object classification framework one has to feed the resulting histograms into a classification algorithms. Either generative or discriminative methods can be used. Below the main steps of BoW classification processing pipeline will be disscussed.

\subsection{Detection}

	Numerous keypoint detectors have been developed.

\subsection{Description}
\subsection{Vector Quantization}
\subsection{Classification}
